---
title: "607 Project1 Hui Gracie Han Sep23"
output: html_document
---

In this project, you're given a text file with chess tournament results where the information has some structure. Your job is to create an R Markdown file that generates a .CSV file (that could for example be imported into a SQL database) with the following information for all of the players:Player's Name, Player's State, Total Number of Points, Player's Pre-Rating, and Average Pre Chess Rating of Opponents
```{r}
library (stringr)
library (readr)
library (dplyr)
library (tidyr)
library (knitr)
```
Read Raw text data into 
```{r}
    TournamentRaw = readLines ("E:/tournamentinfo.txt")
#print(TournamentRaw[1:15],)

```
Since there are seperators as ---------, we used replace function to replace - into empty space
```{r}
TournamentRaw2  = str_replace_all(TournamentRaw ,"-","") 
#print(TournamentRaw2[1:15],)
```
# Read cleaned data into a data frame and write a temporary CSV file to better understand the data
```{r}
TournamentRaw3 = read.delim(textConnection(TournamentRaw2),header = F, sep = "|", stringsAsFactors = F) 
print (TournamentRaw3)

#write_csv(TournamentRaw3, "E:/TournamentRaw3.csv")
```
As we can see, dol11 is all NA, this column is not needed 
```{r}
Tournament4 = TournamentRaw3[,-11]
print (Tournament4 [1:10], )
```
Remove the white space within some of the data elements, such as W   39 will become W39
```{r}
TournamentRow1 = trimws(as.character(Tournament4[1,] ) )
TournamentRow1
                        
TournamentRow2 = trimws(as.character(Tournament4[2,]) )
TournamentRow2
```
```{r}

```
Put row1 and row2 together, because they are technically the herder
```{r}
HeaderT = paste(TournamentRow1, TournamentRow2)
HeaderT

```

```{r}
Tournament6 = as.tbl(Tournament4[-1:-2,])
names(Tournament6) = HeaderT
print (Tournament6)

# Tournament6 is a tibble
write_csv(Tournament6, "E:/Tournament6.csv")


```
